---
title: "Machine Learning Assignment"
author: "Thomas Kliem"
date: "20 June 2015"
output: html_document
---

Read in the data sets.

```{r}

library(caret)
train <- read.csv("pml-training.csv")
test <- read.csv("pml-testing.csv")

```

Define a function to tidy the training data, which will also be run on the test data. The split the training data into training and test sets.

Note, in this assignment, the "test" data is for submission only. The training set will be split into a training and CV set, which will be used to check the model.



```{r}
tidydata <- function(dataset){
  temp <- !(is.na(dataset[1,]) | dataset[1,] == "")
  temp <- dataset[,temp]
  temp <- temp[(temp$new_window=="no"),]
  temp <- temp[,c(-1,-2,-3,-4,-5,-6,-7)]
  return(temp)
}


tidy.data <- tidydata(train)
tidy.test <- tidydata(test)

split <- createDataPartition(y=tidy.data$class,p=0.75,list=FALSE)
tidy.train <- tidy.data[split,]
tidy.CV <- tidy.data[-split,]

```

Define how the model will run with 5 fold cross-validation, and build the model using the caret random forests algorithm.

```{r}

train_control <- trainControl(method="cv",5)
modelrf <- train(classe ~., data=tidy.train, trControl=train_control,method="rf")
```

The model has an estimated error rate of 0.6%

Check the accuracy of the model using the CV test set.
```{r}
pr <- predict(modelrf,newdata=tidy.CV)

confusionMatrix(tidy.CV$classe,pr)
```

This is good.




Use the test examples and submit for grading.

```{r}

test.pr <- predict(modelrf,newdata=tidy.test)


pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}

pml_write_files(test.pr)



```